Syntax-Based Concept Alignment for Domain-Specific Machine Translation

### 2021-05-14 paper/paper.tex
improved tables

\begin{table*}[h]
  \centering
  \begin{tabular}{r|c|c|c|c|c|c}
  \multicolumn{1}{l|}{\textbf{}} & \multicolumn{2}{c|}{\textbf{CE}} & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}fast\_align (100)\end{tabular}}} & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}fast\_align (1000)\end{tabular}}} \\ \hline
  \multicolumn{1}{l|}{}          & \textbf{en-it}  & \textbf{en-sv} & \textbf{en-it}                              & \textbf{en-sv}                              & \textbf{en-it}                                & \textbf{en-sv} \\ \hline  
  \textbf{tot. alignments}        & 536             & 638            & 1242                                        & 1044                                        & 1286                                          & 1065          \\ 
  \textbf{+ and =}                & 392 (73\%)      & 514 (80\%)     & 346 (28\%)                                  & 538 (52\%)                                  & 540 (42\%)                                    & 677 (64\%)    \\ 
  \textbf{+}                      & 363 (68\%)      & 503 (79\%)     & 316 (25\%)                                  & 525 (50\%)                                  & 510 (40\%)                                    & 666 (63\%)    \\ 
  \end{tabular}
  \caption[Comparison between our grammar-based CE module and \texttt{fast\_align}]{Comparison between our grammar-based CE module and \texttt{fast\_align} on PUD data. The middle column shows the results obtained by training \texttt{fast\_align} on the 100-sentence subset fed to the extraction module. On the right, the results obtained by training \texttt{fast\_align} on the full PUD treebanks dataset, discarding the alignments obtained for sentences 101-1000 for the final comparison. Row 1 reports the total number of distinct alignments obtain. Rows 2 and 3 give the percentages of correct alignments, with and without considering sentence pair-specific correspondences as correct.}
  \label{pud_fast}
  \end{table*}

@@

@@

\begin{table*}[h]
  \centering
  \begin{tabular}{r|c|c|c|c}
  \multicolumn{1}{l|}{\textbf{}} & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}PUD (100 sentences)\end{tabular}}} & \multicolumn{2}{c}{\textbf{course plans}}                                                                                                                      \\ \hline
  \multicolumn{1}{l|}{}          & \textbf{en-it}                               & \textbf{en-sv}                               & \textbf{\begin{tabular}[c]{@{}c@{}}DMI (en-it)\\ (881 sentences)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}CSE (en-sv)\\ (539 sentences)\end{tabular}} \\ \hline
  \textbf{tot. alignments}        & 1197                                         & 1325                                         & 1823                                                                           & 1950                                                                           \\
  \textbf{+ and =}                & 916 (77\%)                                   & 1112 (85\%)                                  & 1205 (66\%)                                                                    & 1296 (66\%)                                                                    \\
  \textbf{+}                      & 880 (74\%)                                   & 1099 (84\%)                                  & 1157 (63\%)                                                                    & 1248 (64\%)                                                                    \\
  \end{tabular}
  \caption{TODO:}
  \label{raw_fast}
  \end{table*}

 % TODO: discussion
\todo{add results discussion}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{l|ll}
  \textbf{}            & \textbf{DMI (en-it)} & \textbf{CSE (en-sv)} \\ \hline
  \textbf{BLEU-1 to 4} & 55         & 61         \\ 
  \textbf{BLEU-1 to 3} & 63         & 68         \\ 
  \textbf{BLEU-1 to 2} & 70         & 74          \\
  \textbf{BLEU-1}      & 79         & 81         \\ 
  \end{tabular}
  \caption[BLEU scores for automatic translations based on the course plans grammars]{BLEU scores obtained by comparing one candidate automatic translation per sentence to a reference translation obtained by making the necessary corrections to the automatically generated ones. Both the initial English sentences and their automatic translations were generated using the two course plans grammars.}
  \label{tableu}
\end{table}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{l|ll}
  \textbf{}                                                                   \textbf{type of errors}                 & \textbf{DMI (en-it)} & \textbf{CSE (en-sv)} \\ \hline
  \begin{tabular}[c]{@{}l@{}}\textbf{semantical}\end{tabular}               & 23 (46\%)    & 23 (46\%)    \\ 
  \begin{tabular}[c]{@{}l@{}}\textbf{grammatical}\end{tabular}             & 10 (20\%)      & 3 (6\%)      \\ 
  \begin{tabular}[c]{@{}l@{}}\textbf{semantical and} \\ \textbf{grammatical}\end{tabular} & 3 (6\%)      & 4 (8\%)      \\ 
  \end{tabular}
  \caption[Types of errors encountered in the automatically translated sentences]{Number of automatically translated sentences containing only semantical, only grammatical and both semantical and grammatical errors in the two synthetic course plans corpora.}
  \label{obs}
\end{table}

>>>>

\begin{table*}[h]
  \centering
  \begin{tabular}{r|c|c|c|c|c|c}
  \multicolumn{1}{l|}{\textbf{}} & \multicolumn{2}{c|}{\textbf{CE}} & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}\texttt{fast\_align} \\(100 sentences)\end{tabular}}} & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}\texttt{fast\_align} \\(full dataset)\end{tabular}}} \\ \hline
  \multicolumn{1}{l|}{}          & \textbf{en-it}  & \textbf{en-sv} & \textbf{en-it}                              & \textbf{en-sv}                              & \textbf{en-it}                                & \textbf{en-sv} \\ \hline  
  \textbf{distinct alignments}        & 536             & 638            & 1242                                        & 1044                                        & 1286                                          & 1065          \\ 
  \textbf{correct (\texttt{+} and \texttt{=})}                & 392 (73\%)      & 514 (80\%)     & 346 (28\%)                                  & 538 (52\%)                                  & 540 (42\%)                                    & 677 (64\%)    \\ 
  \textbf{usable in MT (\texttt{+})}                      & 363 (68\%)      & 503 (79\%)     & 316 (25\%)                                  & 525 (50\%)                                  & 510 (40\%)                                    & 666 (63\%)    \\ 
  \end{tabular}
  \caption[Word alignment comparison between our grammar-based CE module and \texttt{fast\_align}]{Comparison between our grammar-based CE module and \texttt{fast\_align} on PUD data. The middle column shows the results obtained by training \texttt{fast\_align} on the 100-sentence subset also fed to the extraction module. On the right, the results obtained by training it on the full dataset, discarding the alignments obtained for sentences 101-1000 for the final comparison.}
  \label{pud_fast}
  \end{table*}

@@

\begin{table*}[h]
  \centering
  \begin{tabular}{r|c|c|c|c}
  \multicolumn{1}{l|}{\textbf{}} & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}PUD (100 sentences)\end{tabular}}} & \multicolumn{2}{c}{\textbf{course plans}}                                                                                                                      \\ \hline
  \multicolumn{1}{l|}{}          & \textbf{en-it}                               & \textbf{en-sv}                               & \textbf{\begin{tabular}[c]{@{}c@{}}DMI (881 sentences)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}CSE (539 sentences)\end{tabular}} \\ \hline
  \textbf{disrinct alignments}        & 1197                                         & 1325                                         & 1823                                                                           & 1950                                                                           \\
  \textbf{correct (\texttt{+} and \texttt{=})}                & 916 (77\%)                                   & 1112 (85\%)                                  & 1205 (66\%)                                                                    & 1296 (66\%)                                                                    \\
  \textbf{usable in MT (\texttt{+}})                      & 880 (74\%)                                   & 1099 (84\%)                                  & 1157 (63\%)                                                                    & 1248 (64\%)                                                                    \\
  \end{tabular}
  \caption{Comparison the extraction of alignments of any size from manually annotated PUD treebanks and automatically parsed sentences from the course plans corpora.}
  \label{raw_fast}
  \end{table*}

@@

@@

\begin{table}[h]
  \centering
  \begin{tabular}{r|cc}
  \textbf{}            & \textbf{DMI (en-it)} & \textbf{CSE (en-sv)} \\ \hline
  \textbf{BLEU-1 to 4} & 55         & 61         \\ 
  \textbf{BLEU-1 to 3} & 63         & 68         \\ 
  \textbf{BLEU-1 to 2} & 70         & 74          \\
  \textbf{BLEU-1}      & 79         & 81         \\ 
  \end{tabular}
  \caption[BLEU scores for automatic translations based on the course plans grammars]{BLEU scores for automatic translations based on the course plans grammars.}
  \label{tableu}
\end{table}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{r|cc}
  \textbf{}                                                                                    & \textbf{DMI (en-it)} & \textbf{CSE (en-sv)} \\ \hline
  \begin{tabular}[c]{@{}l@{}}\textbf{semantical}\end{tabular}               & 23 (46\%)    & 23 (46\%)    \\ 
  \begin{tabular}[c]{@{}l@{}}\textbf{grammatical}\end{tabular}             & 10 (20\%)      & 3 (6\%)      \\ 
  \begin{tabular}[c]{@{}l@{}}\textbf{both}\end{tabular} & 3 (6\%)      & 4 (8\%)      \\ 
  \end{tabular}
  \caption[Types of errors encountered in the automatically translated sentences.]{Types of errors encountered in the automatically translated sentences.}
  \label{obs}
\end{table}
